{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed

### 2017-04-28 bmvc_review.tex
Revised the introduction.

One of the dominant frameworks for online object tracking is the
correlation filter that essentially solves a single-target tracking
problem as a regression problem in the frequency domain. This
framework assumes that the target location is given at the very first
image frame like other online tracking algorithms
\cite{smeulders2014survey}. Given this positive example for the
regression problem, a set of negative examples is collected around the
initial, target bounding box and represented as a circulant matrix
\cite{henriques2015high}. One can optimally solve this regression
problem using a ridge regression in a closed form. However, such a
solution involves in expensive matrix operations
$\mathcal{O}(n^{3})$. The correlation filter offers a less complex
solution, $\mathcal{O}(n\log n)$ over element-wise multiplication in a
frequecny domain \cite{bolme2010visual,henriques2015high}. Thank to
this reformulation, a complete pipeline of an object tracker based on
the correlation filter can be easily implemented and run very
efficiently in an online fashion. In fact, a variant of the
correlation filter, kernelized correlation filter with multi-channel
features, outperformed other state-of-the-art tracking algorithms in
VOT15 challenge, in terms of run-time and tracking accuracy. However,
the vanilla form of such an online tracker is prone to drift, and
fails to track a target over a long period of time primarily
\cite{henriques2015high} because of the dilemma of
stability-plasticity in updating appearance model, where the
appearance model will be overfitted to only the images used to train
and a compromise on the frequency of updating the model is carefully
implemented \cite{santner2010prost}. For example, a naive way of
handling a scale change of a target could reduce the run-time
performance from 300 to 100 fps. A seemingly obvious way of addressing
the scale change is to scan the region of interest (ROI) with
templates in different dimensions based on pre-defined scale ratios to
find the target
\cite{henriques2015high,tang2015multi,ma2015long,bibi2015multi,li2014scale}. However,
because of computational nature of correlation filter, this approach
would merely increase the computational complexity of tracking by
running detection with multiple templates.

@@

The contributions of this study are as follows.
\begin{itemize}

\item \textbf{Novel Single-Target Tracking in High-Speed for Long-Term
  Tracking} To be practical, the execution time of an object tracking
  is important. We proposed a new object tracking algorithm that is a
  collection of kernelized correlation filters (KCF). Each of KCFs is
  designed to address two challenges of object tracking: scale and
  translation. We also incorporate a Bayes filter to prevent from
  being drift.

>>>>

One of the dominant frameworks for online object tracking is the
correlation filter that essentially solves a single-target tracking
problem as a regression problem in the frequency domain. This
framework assumes that the target location is given at the very first
image frame like other online tracking algorithms
\cite{smeulders2014survey}. Given this positive example for the
regression problem, a set of negative examples is collected around the
initial, target bounding box and represented as a circulant matrix
\cite{henriques2015high}. One can optimally solve this regression
problem using a ridge regression in a closed form. However, such a
solution involves in expensive matrix operations
$\mathcal{O}(n^{3})$. The correlation filter offers a less complex
solution, $\mathcal{O}(n\log n)$ over element-wise multiplication in a
frequecny domain \cite{bolme2010visual,henriques2015high}. Thank to
this reformulation, an object tracking pipeline based on the
correlation filter can be easily implemented and run very efficiently
in an online fashion. In fact, a variant of the correlation filter,
the kernelized correlation filter with multi-channel features
\cite{henriques2015high} showed impressive object trackin results and
outperformed other state-of-the-art tracking algorithms, for example,
in VOT15 challenge, in terms of run-time and tracking
accuracy. However, the vanilla form of such an online tracker is prone
to drift, and fails to track a target over a long period of time
primarily \cite{henriques2015high} because of the dilemma of
stability-plasticity in updating appearance model, where the
appearance model will be overfitted to only the images used to train
and a compromise on the frequency of updating the model is carefully
implemented \cite{santner2010prost}. For example, a naive way of
handling a scale change of a target could reduce the run-time
performance from 300 to 100 fps. A seemingly obvious way of addressing
the scale change is to scan the region of interest (ROI) with
templates in different dimensions based on pre-defined scale ratios to
find the target
\cite{henriques2015high,tang2015multi,ma2015long,bibi2015multi,li2014scale}. Due
to the computational nature of correlation filter, however, this
approach would merely increase the computational complexity because it
has to run the correlation filter multiple times on each frame.

@@

The contributions of this study are as follows.
\begin{itemize}
\item \textbf{Novel Single-Target Tracking in a Very High-Speed} Our
  algorithm, {\it E}nKCF, deploys an ensemble of KCF in turn to more
  efficiently address the scale variance and the dynamic maneuver of a
  target while perserving run-time performance as high as possible. To
  minimize any potential performance gap from transiting one KCF to
  another, we use a Bayes filter.
